Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-07-03 survey/survey.tex
add various comments which act as a set of TODOs.

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. The first
says that sequential composition itself ($\odot$) is associative.
The next $4$ capture how
the $\oplus$ and $\otimes$ combinators ``commute'' with re-association.
In other words, it expresses the type-level associativity of $+$ is
properly reflected by the properties of $\oplus$.
The last two equivalences show how composition of associativity combinators
interact together. 
\begin{comment}
For example, the last equivalence captures the idea that the
program $\assocrt \odot \assocrt$ transforms an input of
type $((t_1 * t_2) * t_3) * t_4$ to an output of type
$t_1 * (t_2 * (t_3 * t_4))$ as follows:

@@

\jc{need to find some combinators whose diagrams can help illustrate 
the ideas further. Enough so that the next paragraph makes sense.}

\noindent This of course gives rise to a \emph{critical pair} in words over the
level-1 language, as both of these programs are between the same types.
Since neither of these involve either trivial types (like $0$ or $1$) nor
twists (i.e. automorphisms) on the types themselves, coherence requires that
these in fact be equivalent programs.  One interpretation is that
\emph{outermost} re-associations is the same as \emph{innermost}
re-associations.

@@

We can do for the level-2 combinators the same as was done for level-1:
create a programming language with these combinators as fundamental
constants, typed by level-1 combinators. But we can do more, as these
new combinators are exactly rewrites for level-1 programs.  Thus,
it is possible to create

@@

>>>>

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. The first
says that sequential composition itself ($\odot$) is associative.
The next $4$ capture how
the $\oplus$ and $\otimes$ combinators ``commute'' with re-association.
In other words, it expresses the type-level associativity of $+$ is
properly reflected by the properties of $\oplus$.
The last two equivalences show how composition of associativity combinators
interact together.

\jc{Say that the bottom line in Fig.~\ref{figj} is actually the
pentagon diagram of monoidal categories. Draw it, and label it
using our combinators instead of the usual ones.}

\begin{comment}
For example, the last equivalence captures the idea that the
program $\assocrt \odot \assocrt$ transforms an input of
type $((t_1 * t_2) * t_3) * t_4$ to an output of type
$t_1 * (t_2 * (t_3 * t_4))$ as follows:

@@

@@

\jc{Maybe interpret the next level as simply term rewriting?
We already know the start and end, but if we also have a whole
sequence of `trans', then we can reconstruct the whole thing
from that. In other words, the example below could be
reconstructed from the start, end and the program itself,
erasing all of the lhs annotations, which are merely there for
humans to track.}

@@

\jc{The above is, up to uses of assoc, a linear notation for a
commutative diagram. So draw it.}
